### 2023-05-11 main.tex
Adjusted spacing of title page
Fixed some typos in main abstract

\begin{titlepage}
\begin{center}
    Finding structure in disorder: Evolutionary analyses of disordered proteins in \textit{Drosophila}\\
    \bigskip
    By\\
    Marc Singleton\\
    \vfill
    A dissertation submitted in partial satisfaction of the\\
    requirements for the degree of\\
    Doctor of Philosophy\\
    in\\
    Biophysics\\
    in the\\
    Graduate Division\\
    of the\\
    University of California, Berkeley\\
    \vfill
    Committee in charge:\\
    Professor Mike Eisen, Chair\\
    Professor Liana Lareau\\
    Professor Susan Marqusee\\
    Professor Priya Moorjani\\
    \bigskip
    Spring 2023\\
\end{center}
\end{titlepage}

@@

Thus, in the first chapter I develop a novel method for identifying orthologs which addresses this shortcoming and apply it to 33 \textit{Drosophila} genomes to generate a set of aligned orthologs. In the second chapter I then identify rapidly evolving IDRs in these alignments and analyse them with a variety of evolutionary models dissect the forces driving their evolution and detect patterns of conservation. Finally, in the third chapter I discuss several software tools and tutorials for fitting statistical models to data, which were created while pursuing the previous aims.

>>>>

\begin{titlepage}
\begin{center}
    Finding structure in disorder: Evolutionary analyses of disordered proteins in \textit{Drosophila}\\
    \bigskip
    By\\
    \bigskip
    Marc Singleton\\
    \vfill
    A dissertation submitted in partial satisfaction of the\\
    requirements for the degree of\\
    Doctor of Philosophy\\
    in\\
    Biophysics\\
    in the\\
    Graduate Division\\
    of the\\
    University of California, Berkeley\\
    \vfill
    Committee in charge:\\
    Professor Mike Eisen, Chair\\
    Professor Liana Lareau\\
    Professor Susan Marqusee\\
    Professor Priya Moorjani\\
    \bigskip
    Spring 2023\\
\end{center}
\end{titlepage}

@@

Thus, in the first chapter, I develop a novel method for identifying orthologs which addresses this shortcoming and apply it to 33 \textit{Drosophila} genomes to generate a set of aligned orthologs. In the second chapter, I then identify rapidly evolving IDRs in these alignments and analyse them with a variety of evolutionary models to dissect the forces driving their evolution and detect patterns of conservation. Finally, in the third chapter, I discuss several software tools and tutorials for fitting statistical models to data, which were created while pursuing the previous aims.
